Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-22 manuscript_covid19dashboard.Rmd
Updated paper

University of Sri Jayewardenepura, Sri Lanka, CO10230

@@

The rest of the paper is organized as follows: the [Section 2](#litreview) of dashboards created using data related to COVID-19 pandemic. [Section 3](#methods) provides the methodology; [Section 4](#results) presents results; and [Section 5](#conclusion) offers some concluding remarks.

>>>>

@@

The rest of the paper is organized as follows: the [Section 2](#litreview) of dashboards created using data related to COVID-19 pandemic. [Section 3](#methods) provides the methodology and basic design concept; [Section 4](#results) presents results; and [Section 5](#conclusion) offers some concluding remarks.

### 2022-04-22 manuscript_covid19dashboard.tex
Updated paper

The rest of the paper is organized as follows: the
\protect\hyperlink{litreview}{Section 2} of dashboards created using
data related to COVID-19 pandemic. \protect\hyperlink{methods}{Section
3} provides the methodology; \protect\hyperlink{results}{Section 4}
presents results; and \protect\hyperlink{conclusion}{Section 5} offers
some concluding remarks.

>>>>

The rest of the paper is organized as follows: the
\protect\hyperlink{litreview}{Section 2} of dashboards created using
data related to COVID-19 pandemic. \protect\hyperlink{methods}{Section
3} provides the methodology and basic design concept;
\protect\hyperlink{results}{Section 4} presents results; and
\protect\hyperlink{conclusion}{Section 5} offers some concluding
remarks.
